---
title: "HOMEWORK 1 GROUP 11   IE5374 19939 ST: Foundations Data Analytics"  
Contribution: (34%-Vidyun AKila Sundhara Raaman, 33%-Shubham Patidar, 33%-Himani Thakker)
output: pdf_document
---

**importing dataset**
```{r}
library(dplyr)
library(lubridate)
library(tidyr)
library(magrittr)
library(stringr)
fm <- read.csv('fm.csv', na.strings = "")         # reading file from the database

```

**Task 1.1**
Compute the number of farmers market in the United States
```{r}
nrow(fm)                                          # provides number of rows and hence number of farmer markets
```

**Task 1.2**
Write a code to compute the number of farmers markets by state and arrange
them in descending order of number of farmers market.
```{r}
states <- fm$State                                #extracting all the states in a vector.

unique_find=function(a){                          #creating own function for extracting unique values
  vec1=vector()
  
  c=1
  for (i in a){
    if(!(i %in% vec1)){
      vec1[c]=i
      c=c+1
      
      
    }
    
  }
  vec1
    
}


unistate=unique_find(states)                      # creating another object for storing unique states.

vec <- vector()

for (i in 1:length(unistate)){                    # Creating a list to count the occurance of each element in unique
     c=0

      for( j in 1:length(states))

      {

        if(unistate[i] == states[j])

          {

          c = c+1

          }
      }

      vec[i]=c

}

df1 <- data.frame(unistate,vec)                   # creating the dataframe to store it


sorting=function(a){                              # creating my own sorting function

  vec=vector()

  for (i in 1:length(a)){

    mx=which.max(a)

    vec[i]=mx

    a[mx]=NA

  }
  vec

}


df1[sorting(df1$vec) ,]   


```

**Task 1.3**
Write a code to compute the number of farmers market by cities in
Massachusetts and display the top five cities.
```{r}
df_mass=fm[which(fm$State=="Massachusetts"),]     #Filtering the data      

unicity=unique_find(df_mass$city)                 #Finding the unique values in it

vec <- vector()


for (i in 1:length(unicity)){                     #Finding the count of each occurance
     c=0

      for( j in 1:length(df_mass$city))

      {
        if(!is.na(unicity[i]) & !is.na(df_mass$city[j])){
          if(unicity[i] == df_mass$city[j] )
          {

          c = c+1

          }
          
        }

        
      }

      vec[i]=c

}

df1 <- data.frame(unicity,vec)
df1[sorting(df1$vec) ,] [1:5,]
```

**Task 1.4**
Write a code to show the top 5 states by number of farmers market that offers
coffee
```{r}

unistate=unique_find(fm$State)                    #Finding the unique values

v=rep(0,length(unistate))



for (j in 1:nrow(fm)){                            #Incrementing the count if they match
  if(!is.na(fm$Coffee[j]) &!is.na(fm$State[j])){
    
    if(fm$Coffee[j]=="Y"){
      
      ind=which(unistate==fm$State[j])
      v[ind]=v[ind]+1
      
    }
    
    
  }

    
}

sorting=function(a){                            #Creating my own sorting function

  vec=vector()

  for (i in 1:length(a)){

    mx=which.max(a)

    vec[i]=mx

    a[mx]=NA

  }
  vec

}
newdf=data.frame(city=unistate,no_of_market=v)

newdf[sorting(newdf$no_of_market) ,][1:5,]     #Printing the top 5 rows
  

```
**Task 2**
Use the “designation” variable and calculate the number of 20 year old wine in
the dataset
```{r}
wine <- read.csv('wine_data.csv', na.strings = "")
winedate <- wine$designation
library(stringr)
pattern=c("20y","20an","20th")                 # Creating all patterns to match
winedate=gsub("[[:punct:]]"," ",winedate)      #Removing all unwanted symbols
winedate=gsub(" ","",winedate)                 #Removing all spaces
x=grep(paste(pattern,collapse="|"), str_to_lower(winedate), value = TRUE)#Finding all strings which matches the patten
cat("Number of 20 years old wine are",length(x))
```
**Task3**
Write an R code to extract keyword data from the above file and convert it to a
weighted adjacency matrix
```{r}
keyword <- read.csv("E:/GRAD/fda/hw1/Keyword_data - Keyword_data.csv", header=TRUE,na.strings=NA)

fil_key=keyword%>%select(c("Keyword.1":"Keyword.12")) #Filtering the columns
fil_key=fil_key[!apply(fil_key == "", 1, all), ] # Removing rows if they have NA in all columns


fil_key[fil_key==""]="empty" #Replacing "" with empty  

uni=unname(unlist(fil_key[1,])) #Converting dataframe's row 1 into vector



c=length(uni)+1 

for (i in 2:nrow(fil_key)){  #Find all unique keywords and store
  for (j in fil_key[i,]){   
    if(!(j %in% uni)){        
      uni[c]=j
      c=c+1
      
      
      
    }
  }
}

empty_matrix<-matrix(0,length(uni),length(uni)) #create empty matrix of size equals length of unqiue values with 0
colnames(empty_matrix)=uni #Renaming the column and row names in the matrix
rownames(empty_matrix)=uni



for (i in 1:nrow(fil_key)){         #Loop to iterate all articles
  #print(i)
  for (j in unname(unlist(fil_key[i,]))){  #Loop to iterate keyword inside each article
    #print(j)
    for (k in unname(unlist(fil_key[i,])))  # Loop to iterate keywords to make count
      {#print(k)
      if(!(j==k)){
        #cat(j,k,"\n")
        empty_matrix[j,k]=empty_matrix[j,k]+1  # Incrementing the count if two keywords are different
        
        
      }
    }
  }
}

z=empty_matrix[rownames(empty_matrix)!="empty", colnames(empty_matrix)!="empty"] #Removing row and column named empty


print(z)

```




